SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-04 docs/questioning.tex
some additions - changes

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[scale=0.47]{defect-percentages.png}
\end{center}
\caption{\label{fig:defect_sources}A pie showing where the
authors reffered to, to find vulnerabilities to test
their mechanims. We also provide which source was used
by which publication:
{\it Bugtraq}~\cite{PB05,KKVJ06,KJKV09,JEP08},
{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09},
{\sc xss}ed.com~\cite{NSS06,APKLM10},
ha.ckers.org~\cite{TNH07,PSC09,LV09},
Microsoft~\cite{RDWDE07}.}
\end{figure}

Table~\ref{tab:comp} indicates that 27 out of
34 mechanisms were tested on real-world applications
known to be vulnerable. The vulnerabilities
associated with these applications are enlisted
in the following providers: the Common Vulnerabilities
and Exposures ({\sc cve})
database,\footnote{\url{https://cve.mitre.org/}}
the {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}
security mailing list, the
{\sc xss}ed.com\footnote{\url{www.xssed.com}}
security bulletin provider, Microsoft's security
bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
and the ha.ckers.org\footnote{\url{www.xssed.com}}
security bulletin provider. Figure~\ref{fig:defect_sources}
presents how many (in terms of percentages) and which
(in the figure's caption) authors referred to which source.
In numerous occassions authors performed tests based
on the same applications. For instance, 12 mechanisms
were tested on a vulnerable version of
{\sc phpbb}.\footnote{https://www.phpbb.com/}

>>>>

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[scale=0.47]{defect-percentages.png}
\end{center}
\caption{\label{fig:defect_sources}A pie showing where the
authors reffered to, to find vulnerabilities to test
their mechanims. We also provide which source was used
by which publication:
{\it Bugtraq}~\cite{PB05,KKVJ06,KJKV09,JEP08},
{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09,JKK06a},
{\sc xss}ed.com~\cite{NSS06,APKLM10},
ha.ckers.org~\cite{TNH07,PSC09,LV09},
Microsoft~\cite{RDWDE07}.}
\end{figure}

Table~\ref{tab:comp} indicates that 27 out of
34 mechanisms were tested on real-world applications
known to be vulnerable. The vulnerabilities
associated with these applications are enlisted
in the following providers: the Common Vulnerabilities
and Exposures ({\sc cve})
database,\footnote{\url{https://cve.mitre.org/}}
the {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}
security mailing list, the
{\sc xss}ed.com\footnote{\url{www.xssed.com}}
security bulletin provider, Microsoft's security
bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
and the ha.ckers.org\footnote{\url{www.xssed.com}}
security bulletin provider. Figure~\ref{fig:defect_sources}
presents how many (in terms of percentages) and which
(in the figure's caption) authors referred to which source.
In numerous occassions authors performed tests based
on the same applications. For example, 12 mechanisms
were tested on a vulnerable version of
{\sc phpbb}.\footnote{https://www.phpbb.com/}

There are also authors that took a different approach.
For instance, during their initial tests,
Stock et al.~\cite{SLMS14} managed to bypass
the browser-based {\sc xss} filters of the
73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
These vulnerabilities were actually found during
their previous research~\cite{LSJ13}.
